An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-24 intro.tex
some changes to intro

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}. 
However, the resulting image may be too big to distribute. An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
The encapsulation of the self-contained package is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}. While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.

>>>>

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}. 
However, the resulting image may be too big to share or distribute widely. An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package. The encapsulation is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}. However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.

While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result. Often
